---
title: "SDS 315 HW 7"
author: "Prady Kandi"
date: "2025-04-07"
output: pdf_document
---
prk599

The link to the Github repo containing the R file can be found [here](https://github.com/PradyK756/SDS-315-HW7).

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(mosaic)
library(mosaicCore)
library(knitr)
library(mosaic)
library(MatchIt)
```

```{r imports, echo = FALSE}
arms <- read.csv("armfold.csv")
```

```{r}
table(arms$Sex)
```
```{r, echo = FALSE}
male_Lonr <- arms |>
  filter(Sex == "Male") |>
  select(LonR_fold) |>
  summarise(prop_right_on_top = mean(LonR_fold == 0))
```

```{r, echo = FALSE}
female_Lonr<- arms |>
  filter(Sex == "Female") |>
  select(LonR_fold) |>
  summarise(prop_right_on_top = mean(LonR_fold == 0))
```
There are 106 males and 111 females in this dataset. 52.8% of men folded their left arm on top, and 57.7% of women folded theirs on top.

```{r, echo = FALSE}
male_Lonr <- as.numeric(male_Lonr)
female_Lonr <- as.numeric(female_Lonr)

male_Lonr
female_Lonr

diff_prop = male_Lonr - female_Lonr
diff_prop
```
The observed difference between the two groups is 4.8%.
```{r, echo = FALSE}
prop.test(x = c(as.numeric(male_Lonr * 106), as.numeric(female_Lonr * 111)), n = c(106, 111), correct = FALSE)
```
R's function prop_test gives a lower bound of -0.18 and an upper bound of 0.08.
```{r, echo = FALSE}
stan_E = sqrt(( male_Lonr * (1-male_Lonr) /106 ) + ( female_Lonr * (1-female_Lonr)/111 ))
```
To work the standard error out by hand, the formula is the square root of the sum of each proportion.


```{r, echo = FALSE}
low_bound = diff_prop - 1.96 * stan_E
up_bound = diff_prop + 1.96 * stan_E

low_bound
up_bound
```
Multiply by 1.96 since this is the z-score for the 95th percentile..

If we were to take many samples from this dataset and construct confidence intervals, 95% of all intervals would have their true mean lie between -0.1805 and 0.0839.

```{r, echo = FALSE}
stan_E
```

The standard error  of 0.067 is the expected difference between the two proportions. Between multiple samples, this value represents the mean diffmean.

Sampling distribution is a collection of the diff mean of each sample in this context. The sample size will always stay the same, but each will have different data.

The central limit theorem justifies this. 
```{r, echo = FALSE}
votes <- read.csv("turnout.csv")
```

```{r, echo = FALSE}
votes |>
  filter(voted1998 == 1) |>
  group_by(GOTV_call) |>
  summarise(count = n(), .groups = "drop")
```

```{r, echo = FALSE}
voters_noCall <- votes |>
  filter(voted1998 == 1) |>
  select(GOTV_call) |>
  summarise(No_Call = mean(GOTV_call == 0))

voters_Call <- votes |>
  filter(voted1998 == 1) |>
  select(GOTV_call) |>
  summarise(Call = mean(GOTV_call == 1))

voters_noCall <- as.numeric(voters_noCall)
voters_Call <- as.numeric(voters_Call)



```


```{r, echo = FALSE}
stan_E2 = sqrt(( voters_noCall * (1-voters_noCall) /4701 ) + ( voters_Call * (1-voters_Call)/160 ))

diff_prop2 = voters_Call - voters_noCall
```

```{r, echo = FALSE}
low_bound2 = diff_prop2 - 1.96 * stan_E2
up_bound2 = diff_prop2 + 1.96 * stan_E2

low_bound2
up_bound2
```


```{r, echo = FALSE}
corr_1996_1998 <- glm(voted1998 ~ voted1996, family = "binomial", data = votes)
corr_age_1998 <- glm(voted1998 ~ AGE, family = "binomial", data = votes)
corr_MAJORPTY_1998 <- glm(voted1998 ~ MAJORPTY, family = "binomial", data = votes)

summary(corr_1996_1998)
summary(corr_age_1998)
summary(corr_MAJORPTY_1998)
```

```{r, echo = FALSE}
corr_1996_Call <- glm(GOTV_call ~ voted1996, family = "binomial", data = votes)
corr_age_Call <- glm(GOTV_call ~ AGE, family = "binomial", data = votes)
corr_MAJORPTY_Call <- glm(GOTV_call ~ MAJORPTY, family = "binomial", data = votes)

summary(corr_1996_Call)
summary(corr_age_Call)
summary(corr_MAJORPTY_Call)
```


```{r, echo = FALSE}
confint(corr_1996_1998)
confint(corr_age_1998)
confint(corr_MAJORPTY_1998)


confint(corr_1996_Call)
confint(corr_age_Call)
confint(corr_MAJORPTY_Call)
```
```{r, echo = FALSE}
votes_match = matchit(voted1998 ~ AGE + factor(voted1996) + factor(MAJORPTY), data = votes, ratio=5)
votes_matched = match.data(votes_match)
```


